\documentclass[a4paper,11pt,agenda,chair]{meetingmins}

\setcommittee{Thesis on External Range Reporting}

\setmembers{
  \chair{K.~Green},
  P.~Gabrielsen,
  C.~Hansen
}

\setdate{February 29, 2016}

\begin{document}
\maketitle

\section{Since last meeting}
\begin{items}
\item Report
	\begin{items}
		\item Added section to \textit{Theory}: child structure
		\item Added section to \textit{Implementation}: child structure
        \item Added section to \textit{Preliminaries}: B-tree
        \item Added figures of query and sweep line
	\end{items}
\item Coding
	\begin{items}
		\item Child-structure: Finished with extensive testing
		\item Main data structure: Implement boiler plate.
		\item Main data structure: Implement and unit test of \textit{overflowing insertion buffers}
		\item Main data structure: Implement and unit test of \textit{overflowing point buffers}
		\item Main data structure: Implement and unit test of \textit{node degree overflow}
		\item Main data structure: Implement and unit test of \textit{underflowing point buffers}
		\item Main data structure: Implement and integration test of \textit{insertion}
	\end{items}
\end{items}

\section{Plan until next meeting}
\begin{items}
\item Report
	\begin{items}
		\item Finish preliminary section on B-tree
	\end{items}
\item Coding
	\begin{items}
		\item Main data structure: Implement and unit test of \textit{overflowing delete buffer}
		\item Main data structure: Implement and integration test of \textit{deletion}
		\item Main data structure: Implement and integration test of \textit{boostrapping structure}
		\item Main data structure: Implement and integration test of \textit{construction}.
	\end{items}
\end{items}

\section{Questions and remarks}
\begin{items}
	\item Is there are a general \LaTeX~template for theses?
		\begin{items}
			\item Found Anders M\o llers template. Are all items needed? Resum\'e in danish?
		\end{items}
\item Gerth's structure is a B-tree on the $x$ values of points. We can have $\mathcal{O}(B)$ points in a node but only have a fanout of $\mathcal{O}(B^\epsilon)$. How?

\item Bottom up and top down filling of underflowing point buffers. This is vague in the paper.

\end{items}



\section{Bug of the week}
Anders' \LaTeX~template spells Acknowledgements incorrect in table of contents. Almost all theses using his template has this misspelled.
\end{document}
