\documentclass[a4paper,11pt,agenda,chair]{meetingmins}
\usepackage{epigraph}
\setcommittee{Thesis on External Range Reporting}

\setmembers{
  \chair{K.~Green},
  P.~Gabrielsen,
  C.~Hansen
}

\setdate{April Fool's Day, 2016}

\begin{document}
\maketitle

\section{Since last meeting}
\begin{items}
\item Report
	\begin{items}
		\item Main data structure: Theory and analysis (including figures). \\Only few sections missing.
	\end{items}
\item Coding of Brodahls
	\begin{items}
		\item Main data structure: \textsc{Liniear Construction} integration test passed.
		\item Main data structure: \textsc{Query} integration test passed.
		\item Main data structure: \textsc{Fixup} integration test passed.
		\item Main data structure: \textsc{Global Rebuilding} integration test passed.
		\item Main data structure: Added optimization \textsc{metadata} integration test passed.
		\item Main data structure: Added optimization \textsc{"caching"} integration test passed.
		\item Main data structure: Last minute fix: child structure is not kept in main memory.\\ (not integration tested).
		\item Main data structure: Last minute fix: max\_y of child is considered on query.\\ (not integration tested).
	\end{items}
\item Coding of Arges
	\begin{items}
		\item Base B-tree: Insert with splitting of leaves and nodes.
		\item Base B-tree: (Weak) Delete (marks the node as deleted for global rebuilding).
	\end{items}
\end{items}

\section{Plan until next meeting}
\begin{items}
\item Report
	\begin{items}
		\item Main data structure: Document implementation considerations of Brodahls.
		\item Proof reading: Mark approximately 10 pages from report and bring to Kasper.
	\end{items}
\item Coding
	\begin{items}
		\item Main data structure: Integration test of last code changes.
		\item Continue working on Arges external priority search tree.
	\end{items}
\end{items}

\section{Questions and remarks}
\begin{items}
	\item Installation and set-up of test farm: 2 identical machines (slow; 512 MB RAM, 5400 RPM disk) for running experiments and 1 (fast) machine for testing correctness. The farm uses same kernel and library build version.

	\epigraph{Hot in... \\
So hot in herre... \\
So hot in...
}{Nelly lyrics}
	
\end{items}

\end{document}
